(working title) Local Physiological Adaptation in \textit{Mimulus cardinalis}

### 2014-11-15 ms/ms.tex
Worked on ANOVA tables for growth rate data
Worked on analysis, made growth rate ANOVA tables, figures correlating growth with latitude, made refs.bib file, and added some to methods section of ms.tex

\usepackage{geometry}
\geometry{letterpaper}
\usepackage[parfill]{parskip}    			% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{topcapt}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{natbib}

\usepackage{color}

@@

\newcommand{\cdm}[1]{{ \color{magenta} [{\bf{CDM:}} {\em#1}]}} % Chris' comments are in magenta.
\newcommand{\ala}[1]{{ \color{blue} [{\bf{CDM:}} {\em#1}]}} % Amy's comments are in blue.

@@

			Wet: daily/constant irrigation with cooled water
			Dry: start at week \#, gradually decrease watering frequency/level (see Nancy Emery's protocols)

@@

\subsubsection*{Structure}
\subsubsection*{Function}
\subsubsection*{Performance}

Growth rate: leaf expansion rate AND stem elongation rate

\subsubsection*{Floral}

\subsection*{Intrinsic variation}
	% population intercept?
\subsection*{Variation in stress response} % was high temp really stressful?
	% growth rate
	% photosynthetic
	% trait plasticity
	% variation in mortality (do I trust having multiple data points from growth measurements?)

@@

% ANOVA table for LLL growth rate (need to label tables)
\begin{table*}[htbp]
\usefont{T1}{phv}{m}{n}
\fontsize{10}{12}
\selectfont
\textbf{caption} \\ \\
\begin{center}
\begin{tabular}{lccccc}
\toprule

@@

>>>>

\usepackage{geometry}
\geometry{letterpaper}
\usepackage[parfill]{parskip}    			% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{topcapt}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage{color}

@@

\newcommand{\cdm}[1]{{ \color{magenta} [{\bf{CDM:}} {\em#1}]}} % Chris' comments are in magenta.
\newcommand{\ala}[1]{{ \color{blue} [{\bf{ALA:}} {\em#1}]}} % Amy's comments are in blue.

@@

			Wet: daily/constant irrigation with cooled water
			Dry: start at week \#, gradually decrease watering frequency/level

@@

\subsubsection*{Structure}

leaf traits, biomass allometry

\subsubsection*{Function}

photosynthesis

\subsubsection*{Performance}

Growth rate: leaf expansion rate AND stem elongation rate
Biomass (show correlation between growth rate and biomass)

\subsection*{Intrinsic variation}

\cdm{which traits: growth rate, biomass, biomass allometry, leaf traits, photosynthesis?, mortality?}
We tested for Population, Treatment, and Population $\times$ Treatment interactions using mixed model ANOVA with Family included as a random factor. Models were fit by restricted maximum likelihood using lmer from the R package lme4 version 1.0-5 \citep{Bates_etal_2013}. Significant fixed effect terms were selected using a step-wise backward elimination procedure implemented with the step function in the R package lmerTest version 2.0-11 \citep{Kuznetsova_etal_2014}. Denominator degrees of freedom for $F$-tests were estimated using Satterthwaite's approximation. Significant Population effect indicate intrinsic trait differences; significant Population $\times$ Treatment effects indicate population differences in plasticity.

	%

@@

% ANOVA table for LLL growth rate (need to label tables)
\begin{table*}[htbp]
\usefont{T1}{phv}{m}{n}
\fontsize{10}{12}
\selectfont
\textbf{ANOVA table, Longest leaf length growth} \\ \\
\begin{center}
\begin{tabular}{lcccccc}
\toprule

@@

% ANOVA table for height growth rate (need to label tables)
\begin{table*}[htbp]
\usefont{T1}{phv}{m}{n}
\fontsize{10}{12}
\selectfont
\textbf{ANOVA table, height growth} \\ \\
\begin{center}
\begin{tabular}{lcccccc}
\toprule

\input{Tables/Table_heightGrowthAnova.txt}

\subsection*{Latitude versus growth rate}

\begin{figure*}
\centerline{\includegraphics[width=1\textwidth]{Figures/Figure_LLL_Lat.pdf}}
\label{fig:Fig1}
\usefont{T1}{phv}{m}{n}
\fontsize{10}{12}
\selectfont
\textbf{Figure \#} 
\end{figure*}

\begin{figure*}
\centerline{\includegraphics[width=1\textwidth]{Figures/Figure_Height_Lat.pdf}}
\label{fig:Fig1}
\usefont{T1}{phv}{m}{n}
\fontsize{10}{12}
\selectfont
\textbf{Figure \#} 
\end{figure*}

%--------------------------------------------------
% References
%--------------------------------------------------

\setlength{\bibsep}{6pt}
\bigskip

\bibliography{refs}
\bibliographystyle{evolution}
